\documentclass[12pt]{book}

\title{Planning: Organizing SDW20}
\author{Gabriel Faucher}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\chapter{Introduction}
This here, is main main hub for planning SDW20.
I really feel it's necessary to plan everything out so precisely,
because I'm trying to complete the courses at a quicker pace, and also
to get as much out of these courses as I possibly can. I know the way I learn
is quite different from most people, in that I find it very interesting to 
know why things work, and believe it is of the utmost importance to also 
at all times have a full and clear understanding of the \textbf{how} and
\textbf{why} behind my code. This is the main reason why I've elected to 
suplement to information given to me in the classes; I need more in-depth
informational resources, so I'm going to use those to supplement my learning.
All this means I have to do a whole bunch of planning and organizing myself,
regarding which resources I'll use, when I've got to complete them and how
I'm going to apply them. That is the purpose of this 'book'.

\chapter{1\textsuperscript{st} Semester}
This is where I'll be planning everything regarding the first semester.
The semester is split up into sections, that each pertain to a week in 
the semester: this way, I'll have a good idea what I need to do each week 
without micro-managing myself and driving myself mad.
Here is everything I want to have accomplished by the end of this semester:

\begin{itemize}
  \item Complete Forum (Project)
  \item Complete all the PHP Assignments until Semester 2
  \item Complete all the JavaScript Assignments until Semester 2
  \item Complete all the Frontend Assignment for this Semester
  \item Complete \& apply the following set of resources:
  \item If needed, complete all AVO-subjects' assignments
  \item Track all the resources I end up using on Github
  \item Write \& send a motivatinal letter for taking exams earlier
\end{itemize}

\section{Week 42}
The main goal of this week is basically catching up, and starting out.
This planning pertains to only the last couple days of the week, so I decided
not to plan it full with unrealistic goals, but instead to organize my time 
carefully in order to complete all the tasks with high priority.
For example, that motivational letter \textbf{needs} to be sent this weekend
if I want to make any chance of taking exams early.

\begin{itemize}
  \item Forum (Project): Finish Design
  \item Write \& Send Motivatinal Letter to Exam Comission
  \item Finish Project Specification
  \item JavaScript: The Hard Parts - JavaScript Principles, Functions \& Callbacks 
\end{itemize}

\section{Week 43}
This is my week of vacation, which I'll mostly use to get back up to speed.
The main points of focus here are getting the development of my project started,
catching up with the AVO-subjects, and working ahead on the programming-related subjects.

\begin{itemize}
  \item Forum (Project)
    Instead of dividing the project in Frontend, Backend etc., divide it into components:
    Make each page a component for example, and implement every aspect of it on a page-by-page
    basis.    
    \begin{itemize}
      \item Write the project specification \& send it to Reygan, Jeroen \& Adi
      \item Home component: Routes \& Frontend
      \item Admin component: User authentication/authorization & Frontend
    \end{itemize}
  \item JavaScript
    \begin{itemize}
      \item Week 6: Assignment 1
      \item Week 6: Assignment 2
      \item Week 7: Assignment 1
      \item Week 7: Assignment 2
    \end{itemize}
  \item PHP
    \begin{itemize}
      \item Refactor Assignments from 1\textsuperscript{st} Semester
      \item Assignment 17
      \item Assignment 18
      \item Assignment 19
      \item Assignment 20
    \end{itemize}
  \item Frontend
      \begin{itemize}
        \item Design Challenge 1: Design a Blog
        \item HTML Challenge 1: Convert Blog Design to a Webpage
      \end{itemize}
  \item Dutch
    \begin{itemize}
      \item Assignments Week 3
      \item Assignments Week 5
      \item Assignments Week 6
    \end{itemize}
  \item Maths
    \begin{itemize}
      \item Practice Exam Chapter 1
      \item Practice Exam Chapter 2
    \end{itemize}
\end{itemize}
\end{document}
